Responses to reviewers' comments and list of modifications done\\ on paper !!!!!SOROXX paper ID!!!!!\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-16 cover_letter.tex

\documentclass{article}

@@

@@

We are very grateful to the reviewers for having accepted to review our 
work, for the care they took in examining it and their resulting 
comments which have been appreciated in order to improve the quality of
the paper.

Several reviewers noted linguistic issues and terminology/typography 
inconsistencies. We have done our best to carefully proof-read the article,
with the help of a native English speaker.

In the following three sections, we address separately each of
the concerns of our three reviewers.

\section{Comments of the first reviewer}

@@

We are aware that perception is not robust and therefore one of our next steps
is to include a probabilistic layer to the approach (as already mentioned in
the discussion section). We believe though that a robot (specially interacting
with people) should be allowed to make mistakes due to perception noise, or not
to be sure about something (for instance, "I think that..."), which represents
the certainty the robot has about a fact. In the meantime, to overcome
perception errors, the robot provides visual feedback (looking at objects) to
the user when possible and/or verifies the information with the user whenever
is needed (for instance, "do you mean the box\_01"?).

@@

\section{Comments of the second reviewer}

@@

\section{Comments of the third reviewer}

@@

\subsection{``p.8, III.B.Location according to an object: the authors are
kindly referred to the work done by, e.g., K. Sjöö or J. Kelleher''}

>>>>

\documentclass[11pt]{article}
\usepackage[inner=2cm,outer=2cm, top=2cm, bottom=2cm]{geometry}               % See geometry.pdf to learn the layout options. There are lots.

@@

\title{Responses to reviewers' comments and list of modifications done\\ on paper !!!!!SOROXX paper ID!!!!!\\
\LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}}
\author{S\'everin Lemaignan \and Raquel Ros \and E. Akin Sisbot \and Rachid Alami \and Michael Beetz}

@@

\maketitle

The authors would like to thank the reviewers for their constructive feedback that helped us to strengthen the paper.

Below follow our answers to the reviewers’ comments and suggestions. Each answer also indicates the changes made in the paper to address the reviewer’s concern. An important number of language corrections are made, and the paper is proof-read by a native English speaker.

%We are very grateful to the reviewers for having accepted to review our 
%work, for the care they took in examining it and their resulting 
%comments which have been appreciated in order to improve the quality of
%the paper.

%Several reviewers noted linguistic issues and terminology/typography 
%inconsistencies. We have done our best to carefully proof-read the article,
%with the help of a native English speaker.

%In the following three sections, we address separately each of
%the concerns of our three reviewers.

\section{Reviewer 1}
%\section{Comments of the first reviewer}

@@

We are aware that perception is not robust and therefore one of our next steps
is to include a probabilistic layer to the approach (as already mentioned in
the discussion section). We believe though that a robot (specially interacting
with people) should be allowed to make mistakes due to perception noise, or not
to be sure about something (for instance, "I think that..."), which represents
the uncertainty the robot has about a fact. In the meantime, to overcome
perception errors, the robot provides visual feedback (looking at objects) to
the user when possible and/or verifies the information with the user whenever
is needed (for instance, "do you mean the box\_01"?).

@@

\section{Reviewer 2}
% \section{Comments of the second reviewer}

@@

\section{Reviewer 3}
%\section{Comments of the third reviewer}

@@

\subsection{``p.8, III.B.Location according to an object: the authors are
kindly referred to the work done by, e.g., K. Sj\"o\"o or J. Kelleher''}

Kelleher's work, as well as Blisard's, are now correctly cited in the section.
